\documentclass{IOS-Book-Article}
\usepackage[utf8]{inputenc}
\usepackage{graphics}
\usepackage{mathptmx}
\usepackage{soul}\setuldepth{article}
\usepackage{hhline,longtable}
\usepackage{float}
\usepackage{placeins}
\usepackage{multicol}
\usepackage[english]{babel}
\graphicspath{{figures/}}
%\usepackage{hhline, colortbl, longtable}
%\usepackage{times}
%\normalfont
%\usepackage[T1]{fontenc}
%\usepackage[mtplusscr,mtbold]{mathtime}
%
\def\hb{\hbox to 10.7 cm{}}

\begin{document}
	
	\pagestyle{headings}
	\def\thepage{}
	
	\begin{frontmatter}              % The preamble begins here.
		
		
%		%\pretitle{Pretitle}
%		\title{IoT-Based Smart Medicine Dispenser to Control and Supervise Medication Intake\\}
%		
%		\markboth{}{April 2020\hb}
%		%\subtitle{Subtitle}
%		
%		\author[A]{\fnms{Gleiston} \snm{GUERRERO-ULLOA}%
%			\thanks{Corresponding Author: Gleiston Guerrero-Ulloa, Universidad Técnica Estatal de Quevedo, Quito Avenue, Quevedo, Los Ríos, Ecuador. E-mail: gguerrero@uteq.edu.ec}},
%		\author[B]{\fnms{Miguel J.} \snm{Hornos}}
%		,
%		\author[B]{\fnms{Carlos} \snm{Rodríguez-Domínguez}}
%		and
%		\author[A]{\fnms{Ma. Mercedes} \snm{FERNÁNDEZ-COELLO}}
%		
%		\runningauthor{G. Guerrero-Ulloa et al.}
%		\address[A]{Universidad Técnica Estatal de Quevedo, Faculty of Engineering Sciences}
%		\address[B]{University of Granada, Software Engineering Department}
		Please use the Vancouver citing \& reference system, and the National Library of 
Medicine (NLM) style.

Place citations as numbers in square brackets in the text. All publications cited in 
the text should be presented in a list of references at the end of the manuscript. 
List the references in the order in which they appear in the text. Some examples of 
the NLM style:

\medskip
\noindent\ul{Journal article:}\par\noindent
Petitti DB, Crooks VC, Buckwalter JG, Chiu V. Blood pressure levels before dementia. 
Arch Neurol. 2005 Jan;62(1):112-6.

\medskip
\noindent\ul{Paper from a proceedings:}\par\noindent
Rice AS, Farquhar-Smith WP, Bridges D, Brooks JW. Canabinoids and pain. In: Dostorovsky 
JO, Carr DB, Koltzenburg M, editors. Proceedings of the 10th World Congress on Pain; 
2002 Aug 17-22; San Diego, CA. Seattle (WA): IASP Press; c2003. p. 437-68.

\medskip
\noindent\ul{Contributed chapter in a book:}\par\noindent
Whiteside TL, Heberman RB. Effectors of immunity and rationale for immunotherapy. In: 
Kufe DW, Pollock RE, Weichselbaum RR, Bast RC Jr, Gansler TS, Holland JF, Frei~E~3rd, 
editors. Cancer medicine 6. Hamilton (ON): BC Decker Inc; 2003. p. 221-8.

\medskip
\noindent\ul{Book by author(s):}\par\noindent
Jenkins PF. Making sense of the chest x-ray: a hands-on guide. New York: Oxford 
University Press; 2005. 194 p.

\medskip
\noindent\ul{Edited book:}\par\noindent
Izzo JL Jr, Black HR, editors. Hypertension primer: the essentials of high blood pressure. 
3rd ed. Philadelphia: Lippincott Williams \& Wilkins; c2003. 532 p.

\medskip
\noindent\ul{Proceedings:}\par\noindent
Ferreira de Oliveira MJ, editor. Accessibility and quality of health services. Proceedings of 
the 28th Meeting of the European Working Group on Operational Research Applied to Health 
Services (ORAHS); 2002 Jul 28-Aug 2; Rio de Janeiro, Brazil. Frankfurt (Germany): Peter Lang; 
c2004. 287 p.

\section{Illustrations}

\subsection{General Remarks on Illustrations}
The text should include references to all illustrations. Refer to illustrations in the
text as Table~1, Table~2, Figure~1, Figure~2, etc., not with the section or chapter number
included, e.g. Table 3.2, Figure 4.3, etc. Do not use the words ``below'' or ``above''
referring to the tables, figures, etc.

Do not collect illustrations at the back of your article, but incorporate them in the
text. Position tables and figures with at least 2 lines
extra space between them and the running text.

Illustrations should be centered on the page, except for small figures that can fit
side by side inside the type area. Tables and figures should not have text wrapped
alongside.

Place figure captions \textit{below} the figure, table captions \textit{above} the table.
Use bold for table/figure labels and numbers, e.g.: \textbf{Table 1.}, \textbf{Figure 2.},
and roman for the text of the caption. Keep table and figure captions justified. Center
short figure captions only.

The minimum \textit{font size} for characters in tables is 8 points, and for lettering in other
illustrations, 6 points.

On maps and other figures where a \textit{scale} is needed, use bar scales rather than
numerical ones of the type 1:10,000.

\subsection{Quality of Illustrations}
%Use only Type I fonts for lettering in illustrations.
Embed the fonts used if the application provides that option.
Ensure consistency by using similar sizes and fonts for a group of small figures.
To add lettering to figures, it is best to use Helvetica or Arial (sans serif fonts)
to avoid effects such as shading, outline letters, etc.

 Avoid using illustrations
taken from the Web. The resolution of images intended for viewing on a screen is
not sufficient for the printed version of the book.

If you are incorporating screen captures, keep in mind that the text may not be
legible after reproduction.

\subsection{Color Illustrations}
Please note, that illustrations will only be printed in color if the volume editor agrees to
pay the production costs for color printing. Color in illustrations will be retained
in the online (ebook) edition.


\section{Equations}
Number equations consecutively, not section-wise. Place the numbers in parentheses at
the right-hand margin, level with the last line of the equation. Refer to equations in the
text as Eq. (1), Eqs. (3) and (5).

\section{Fine Tuning}

\subsection{Type Area}
\textbf{Check once more that all the text and illustrations are inside the type area and
that the type area is used to the maximum.} You may of course end a page with one
or more blank lines to avoid `widow' headings, or at the end of a chapter.

\subsection{Capitalization}
Use initial capitals in the title and headings, except for articles (a, an, the), coordinate
conjunctions (and, or, nor), and prepositions, unless they appear at the beginning of the
title or heading.

\subsection{Page Numbers and Running Headlines}
You do not need to include page numbers or running headlines. These elements will be
added by the publisher.

\section{Submitting the Manuscript}
Submit the following to the volume editor:

\begin{enumerate}
\item The main source file, and any other required files. Do not submit more than
one version of any item.

\item The source files should compile without errors with pdflatex or latex.

\item Figures should be submitted in EPS, PDF, PNG or JPG format.

\item A high resolution PDF file generated from the source files you submit.
\end{enumerate}

\begin{thebibliography}{99}


\bibitem{r1}
Petitti DB, Crooks VC, Buckwalter JG, Chiu V. Blood pressure levels before dementia. 
Arch Neurol. 2005 Jan;62(1):112-6.

\bibitem{r2}
Rice AS, Farquhar-Smith WP, Bridges D, Brooks JW. Canabinoids and pain. In: Dostorovsky JO, 
Carr DB, Koltzenburg M, editors. Proceedings of the 10th World Congress on Pain;  2002 Aug 
17-22; San Diego, CA. Seattle (WA): IASP Press; c2003. p. 437-68.

\end{thebibliography}